---
title: "Nathan Creek Analyses"
author: "Chris Madsen"
date: "`r Sys.Date()`"
output: html_document
---

```{r, include = F}
# Load in libraries
library(tidyverse)
library(tidyhydat)
library(sf)

knitr::opts_chunk$set(echo=F,warning=F,message = F)
```

```{r download_flow_data}
# Get daily flow data for Nathan Creek and nearby stations.
station_names = c('Nathan Creek near Glen Valley','West Creek near Fort Langley',
  'Salmon river at Seal Kap Farms','Salmon river at 72 Avenue, Langley',
  'Mclennan Creek near Mount Lehman','Gifford Slough near Matsqui')

station_short_names = c("Nathan","West","Salmon_Kap","Salmon_Langley","McLennan","Gifford")

# station_numbers = lapply(station_names, tidyhydat::search_stn_name) |> 
#   bind_rows() |> 
#   dplyr::pull(STATION_NUMBER)
station_numbers = c("08MH084", "08MH098", "08MH089", "08MH090", "08MH082", "08MH073"
)

station_info = data.frame(
  station_names,
  station_short_names,
  station_numbers
)

all_dat = lapply(station_numbers, tidyhydat::hy_daily_flows) |> 
  bind_rows() |> 
  filter(!is.na(Value))
```

```{r get_field_data}
# Field work data from last year
fd22_site_info = openxlsx::read.xlsx('data/Nathan Creek fish 2022.xlsx', sheet = 'Site Summary', startRow = 5) |> 
  as_tibble() |> 
  mutate(lat = str_extract(Lat_Long, '.* N '),
         lon = str_remove(Lat_Long, '.* N ')) |> 
  mutate(lat = str_remove(lat, ' N'),
         lon = str_remove(lon, ' W')) |> 
  mutate(lat = str_replace_all(lat, '\\.', ' '),
         lon = str_replace_all(lon, '\\.', ' ')) |> 
  mutate(lon = paste0('-',lon))

angle2dec <- function(angle) {
  angle <- as.character(angle)
  x <- do.call(rbind, strsplit(angle, split=' '))
  x <- apply(x, 1L, function(y) {
    y <- as.numeric(y)
    y[1] + y[2]/60 + y[3]/3600
  })
  return(x)
}

fd22_site_info = fd22_site_info |> 
  mutate(lat = angle2dec(lat),
         lon = angle2dec(lon)) |> 
  st_as_sf(coords = c('lon','lat'), crs = 4326)
# 
# ggplot() + 
#   geom_sf(data = bcmaps::bc_bound()) + 
#   geom_sf(data = fd22_site_info)

# library(leaflet)
# 
# leaflet() |> 
#   addTiles() |> 
#   addCircleMarkers(data = fd22_site_info)

fd22_flow_values = openxlsx::read.xlsx('data/Nathan Creek fish 2022.xlsx', sheet = 'WSC station Flows', startRow = 3) |> 
  rename(station_id = `Transect.1.(beside.bridge,.in.pool)`) |> 
  filter(!str_detect(station_id,'Transect')) |> 
  mutate(station_id = as.numeric(station_id)) |> 
  as_tibble()
```

Note! Only two stations have data in both time periods: 08MH090 and 08MH098 (Salmon river at 72 Avenue, Langley and West Creek near Fort Langley, respectively).

```{r make_annual_mad_column}
all_dat = all_dat |> 
  mutate(Year = lubridate::year(Date)) |> 
  group_by(STATION_NUMBER,Year) |> 
  dplyr::mutate(mad = mean(Value)) |> 
  ungroup() |> 
  mutate(percent_mad = Value / mad#,
         # relative_change_in_mad = (Value - mad)/mad
         )
```

```{r calculate_60s_to_90s_ave_and_nathan_creek_ave}
# Calculate average flow rates for two time periods (1960-1990, and 1990-2020)
old_ave = all_dat |> 
  filter(lubridate::year(Date) <= 1990) |> 
  # Include Nathan Creek in the average
  filter(STATION_NUMBER %in% c('08MH090','08MH098')) |>
  mutate(Month = lubridate::month(Date, label = T),
         Day = lubridate::day(Date)) |> 
  group_by(Month,Day) |> 
  summarise(mean_percent_mad_neighbours = mean(percent_mad)) |> 
  ungroup()

# Nathan Creek flow data
nathan_data = all_dat |> 
  filter(STATION_NUMBER == station_numbers[1]) |>
  filter(lubridate::year(Date) >= 1960) |> 
  mutate(Month = lubridate::month(Date, label = T),
         Day = lubridate::day(Date)) |> 
  group_by(Month,Day) |> 
  summarise(mean_percent_mad_nathan = mean(percent_mad)) |> 
  ungroup()

# Just find MAD for Nathan's creek for this older time series
nathan_MAD = all_dat |> 
  filter(STATION_NUMBER == station_numbers[1]) |>
  filter(lubridate::year(Date) >= 1960) |> 
  dplyr::summarise(Nathan_MAD = mean(Value)) |> 
  dplyr::pull(Nathan_MAD)

# Join Nathan creek flow data to the average
old_ave = old_ave |> 
  left_join(nathan_data)

```

```{r calculate_90_to_2020_ave}
# Average flow for 1990-2020
recent_ave = all_dat |> 
  filter(lubridate::year(Date) > 1990) |> 
  filter(STATION_NUMBER %in% c('08MH090','08MH098')) |>
  mutate(Month = lubridate::month(Date, label = T),
         Day = lubridate::day(Date)) |> 
  group_by(Month,Day) |> 
  summarise(mean_percent_mad_neighbours = mean(percent_mad)) |> 
  ungroup()
```

Unfortunately, Nathan Creek also has a data gap in its 3 decades of data.
```{r}
nathan_gaps = all_dat |>
  filter(STATION_NUMBER == station_numbers[1]) |>
  filter(lubridate::year(Date) >= 1960)

nathan_gaps |>
  ggplot() +
  geom_histogram(aes(Year))

```

## Flow Plots {.tabset}

### Nathan Creek, 1960-1990

```{r old_flow_plot_just_nathan}
old_ave |> 
  mutate(my_date = lubridate::ymd(paste0('1990-',Month,'-',Day))) |> 
  ggplot(aes(x = my_date)) + 
  geom_line(aes(y = mean_percent_mad_nathan, col = 'Nathan')) +
  geom_line(aes(y = 1), lty = 2, col = 'darkgrey') + 
  scale_x_date(date_labels = '%b',date_breaks = "1 month") + 
  scale_y_continuous(limits = c(0,4)) +
  scale_color_discrete(direction = -1) +
  labs(y = '% Mean Annual Discharge',
       x = '') + 
  labs(col = 'Stream Group') + 
  theme_minimal() +
  scale_y_continuous(labels = scales::label_percent(),
                     breaks = c(0,1,2,4,6)) +
  theme(legend.position = 'bottom')

# iv. Nathan Creek new data (unknown!)
```

### Nathan Creek + Neighbours, 1960-1990

```{r old_flow_plot}
old_ave |> 
  mutate(my_date = lubridate::ymd(paste0('1990-',Month,'-',Day))) |> 
  ggplot(aes(x = my_date)) + 
  geom_line(aes(y = mean_percent_mad_neighbours, col = 'Neighbouring Streams')) +
  geom_line(aes(y = mean_percent_mad_nathan, col = 'Nathan')) +
  geom_line(aes(y = 1), lty = 2, col = 'darkgrey') + 
  scale_x_date(date_labels = '%b',date_breaks = "1 month") + 
  scale_y_continuous(limits = c(0,4)) +
  scale_color_discrete(direction = -1) +
  labs(y = '% Mean Annual Discharge',
       x = '') + 
  labs(col = 'Stream Group') + 
  theme_minimal() +
  scale_y_continuous(labels = scales::label_percent(),
                     breaks = c(0,1,2,4,6)) +
  theme(legend.position = 'bottom')

# iv. Nathan Creek new data (unknown!)
```

### Neighbours, 1990 - 2020
```{r new_flow_plot}
recent_ave |> 
  mutate(my_date = lubridate::ymd(paste0('1990-',Month,'-',Day))) |> 
  ggplot(aes(x = my_date)) + 
  geom_line(aes(y = mean_percent_mad_neighbours, col = 'Neighbouring Streams')) +
  geom_line(aes(y = 1), lty = 2, col = 'darkgrey') + 
  scale_x_date(date_labels = '%b',date_breaks = "1 month") + 
  scale_y_continuous(limits = c(0,4)) +
  labs(y = '% Mean Annual Discharge',
       x = '') + 
  labs(col = 'Stream Group') + 
  theme_minimal() +
  scale_y_continuous(labels = scales::label_percent(),
                     breaks = c(0,1,2,4,6)) +
  theme(legend.position = 'bottom')
```

### West Station, 60-90s vs. 90-20
```{r}
old_west = all_dat |> 
    filter(STATION_NUMBER %in% c('08MH098')) |>
    filter(lubridate::year(Date) < 1990) |>
    mutate(Month = lubridate::month(Date, label = T),
           Day = lubridate::day(Date)) |> 
    group_by(Month,Day) |> 
    summarise(mean_percent_mad = mean(percent_mad)) |> 
    ungroup()

new_west =  all_dat |> 
    filter(STATION_NUMBER %in% c('08MH098')) |>
    filter(lubridate::year(Date) >= 1990) |>
    mutate(Month = lubridate::month(Date, label = T),
           Day = lubridate::day(Date)) |> 
    group_by(Month,Day) |> 
    summarise(new_mean_percent_mad = mean(percent_mad)) |> 
    ungroup()

west_dat = old_west |> 
  left_join(new_west) |> 
  mutate(my_date = lubridate::ymd(paste0('1990-',Month,'-',Day)))

west_dat |> 
  ggplot(aes(x = my_date)) + 
  geom_line(aes(y = mean_percent_mad, col = '1960-1990 mean MAD')) +
  geom_line(aes(y = new_mean_percent_mad, col = '1990-2020 mean MAD')) +
  geom_line(aes(y = 1), lty = 2, col = 'darkgrey') + 
  scale_x_date(date_labels = '%b',date_breaks = "1 month") + 
  scale_y_continuous(limits = c(0,4)) +
  scale_color_discrete(direction = -1) +
  scale_y_continuous(labels = scales::label_percent(),
                     breaks = c(0,1,2,4,6)) +  labs(y = '% Mean Annual Discharge',
       x = '') + 
  labs(col = 'Time Period') + 
  theme_minimal() +
  theme(legend.position = 'bottom')
```

### Salmon Langley Station, 60-90s vs. 90-20
```{r}
old_salmon = all_dat |> 
    filter(STATION_NUMBER %in% c('08MH090')) |>
    filter(lubridate::year(Date) < 1990) |>
    mutate(Month = lubridate::month(Date, label = T),
           Day = lubridate::day(Date)) |> 
    group_by(Month,Day) |> 
    summarise(mean_percent_mad = mean(percent_mad)) |> 
    ungroup()

new_salmon =  all_dat |> 
    filter(STATION_NUMBER %in% c('08MH090')) |>
    filter(lubridate::year(Date) >= 1990) |>
    mutate(Month = lubridate::month(Date, label = T),
           Day = lubridate::day(Date)) |> 
    group_by(Month,Day) |> 
    summarise(new_mean_percent_mad = mean(percent_mad)) |> 
    ungroup()

salmon_dat = old_salmon |> 
  left_join(new_salmon) |> 
  mutate(my_date = lubridate::ymd(paste0('1990-',Month,'-',Day)))

salmon_dat |> 
  ggplot(aes(x = my_date)) + 
  geom_line(aes(y = mean_percent_mad, col = '1960-1990 mean MAD')) +
  geom_line(aes(y = new_mean_percent_mad, col = '1990-2020 mean MAD')) +
  geom_line(aes(y = 1), lty = 2, col = 'darkgrey') + 
  scale_x_date(date_labels = '%b',date_breaks = "1 month") + 
  scale_y_continuous(limits = c(0,4)) +
  scale_color_discrete(direction = -1) +
  scale_y_continuous(labels = scales::label_percent(),
                     breaks = c(0,1,2,4,6)) +  labs(y = '% Mean Annual Discharge',
       x = '') + 
  labs(col = 'Time Period') + 
  theme_minimal() +
  theme(legend.position = 'bottom')
```

### Neighbours in 1960-1990 vs. Neighbours in 1990 - 2020
```{r}
old_ave |> 
  rename(old_mean_percent_mad_neighbours = mean_percent_mad_neighbours) |> 
  left_join(recent_ave |> rename(recent_mean_percent_mad_neighbours = mean_percent_mad_neighbours)) |> 
  mutate(my_date = lubridate::ymd(paste0('1990-',Month,'-',Day))) |> 
  ggplot(aes(x = my_date)) + 
  geom_line(aes(y = old_mean_percent_mad_neighbours, col = '1960-1990 mean MAD')) +
  geom_line(aes(y = recent_mean_percent_mad_neighbours, col = '1990-2020 mean MAD')) +
  geom_line(aes(y = 1), lty = 2, col = 'darkgrey') + 
  scale_x_date(date_labels = '%b',date_breaks = "1 month") + 
  scale_y_continuous(limits = c(0,4)) +
  scale_color_discrete(direction = -1) +
  scale_y_continuous(labels = scales::label_percent(),
                     breaks = c(0,1,2,4,6)) + 
  labs(y = '% Mean Annual Discharge',
       x = '') + 
  labs(col = 'Time Period') + 
  theme_minimal() +
  theme(legend.position = 'bottom')
```

### Percent Change in Percent MAD from 1960-1990 to 1990-2020 for Neighbour Streams
```{r}
change_in_ave = recent_ave |> 
  left_join(old_ave |> 
              dplyr::rename(old_mean_percent_mad_neighbours = mean_percent_mad_neighbours)) |> 
  mutate(percent_change = 100*(mean_percent_mad_neighbours - old_mean_percent_mad_neighbours)/old_mean_percent_mad_neighbours) |> 
  mutate(nathan_predicted = mean_percent_mad_nathan  + mean_percent_mad_nathan *percent_change/100)
```

```{r}
change_in_ave |> 
  mutate(my_date = lubridate::ymd(paste0('1990-',Month,'-',Day))) |> 
  mutate(change_type = ifelse(percent_change > 0, 'Increase','Decrease')) |> 
  ggplot(aes(x = my_date)) + 
  geom_ribbon(aes(ymin = 0, ymax = 125), alpha = 0.25, fill = 'lightblue') + 
  geom_ribbon(aes(ymin = 0, ymax = -50), alpha = 0.25, fill = 'pink') + 
  geom_point(aes(y = percent_change, col = change_type)) +
  geom_line(aes(y = percent_change), col = 'black') +
  scale_x_date(date_labels = '%b',date_breaks = "1 month") + 
  # scale_y_continuous(limits = c(0,4)) +
  labs(y = 'Percent Change in Percent MAD',
       x = '') + 
  theme_minimal() +
  theme(legend.position = 'bottom')
```

### Predicted Mean MAD for Nathan Creek, 1990 - 2020
```{r}

# # Raw flow record (in m3 ^ s)
# oct_3_2022_single_value = 0.0181 
#   
# # Convert to % mean MAD for Oct 2nd
# oct_3_2022_percent_MAD = oct_3_2022_single_value / change_in_ave |> 
#     dplyr::filter(Month == 'Oct',
#                   Day == 2) |> 
#     pull(nathan_predicted)

# Note that these were actually measured in 2023.
ground_truthed_points = data.frame(
  date_measured = c('1990-07-19','1990-07-20','1990-07-20',
                    '1990-07-20','1990-07-21'),
  site_number = c("23","44","70","88.2","98"),
  discharge_L_s = c(73.34,51.64,14.21,58.92,6.18)
) |> 
  dplyr::mutate(discharge_as_perc_MAD = discharge_L_s/(1000*nathan_MAD)) |> 
  dplyr::mutate(my_date = lubridate::ymd(date_measured))

change_in_ave |> 
  mutate(my_date = lubridate::ymd(paste0('1990-',Month,'-',Day))) |> 
  # mutate(change_type = ifelse(percent_change > 0, 'Increase','Decrease')) |>
  ggplot(aes(x = my_date)) + 
  # geom_point(aes(y = percent_change, col = change_type)) +
  geom_line(aes(y = mean_percent_mad_nathan, col = 'Nathan (1960-1990)'), lwd = 1) +
  geom_line(aes(y = nathan_predicted, col = 'Nathan, Predicted (1990-2020)'), lwd = 1) +
  geom_line(aes(y = 1), lty = 2, col = 'darkgrey') + 
  geom_point(data = ground_truthed_points,
             aes(x = my_date,
                 y = discharge_as_perc_MAD),
             col = 'red') +
  scale_x_date(date_labels = '%b',date_breaks = "1 month") + 
  scale_y_continuous(labels = scales::label_percent(),
                     breaks = c(0,1,2,4,6)) +
  # scale_y_continuous(limits = c(0,4)) +
  labs(y = 'Predicted % Mean Annual Discharge',
       x = '',
       title = 'Predicted, Historical Nathan Creek flow and 2023 ground-truthed flow data (red dots)',
       subtitle = 'Nathan Creek mean MAD predicted using % change in mean MAD of neighbouring streams',
       color = 'Time Period') + 
  theme_minimal() +
  theme(legend.position = 'bottom')
```

Ground-truthed points (red) that were taken in 2023 are noticeably lower than the predicted percent Mean Annual Discharge. 

```{r}
knitr::kable(
  ground_truthed_points |> 
    dplyr::mutate(date_measured = str_replace(date_measured,'1990','2023')) |> 
    dplyr::select(-my_date)
)
```


### Predicted Discharge in Litres per second for Nathan Creek
```{r}

new_Nathan_Creek_MAD = change_in_ave |> 
  mutate(my_date = lubridate::ymd(paste0('1990-',Month,'-',Day))) |> 
  dplyr::mutate(nathan_pred_L_s = nathan_predicted*nathan_MAD*1000) |>
  dplyr::select(my_date, nathan_pred_L_s) |> 
  dplyr::summarise(new_nathan_MAD = mean(nathan_pred_L_s)) |> 
  dplyr::pull(new_nathan_MAD)

```

Water Survey Canada data for Nathan Creek spans 1960 - 1990 (with some gaps), and the mean annual discharge (MAD) according to those data was `r round(nathan_MAD*1000,0)` Litres/second.

The predicted 1990-2020 MAD for Nathan Creek, estimated using the percent change of two of its neighbouring streams, is `r round(new_Nathan_Creek_MAD,0)` Litres/second.

```{r predict_nathan_creek_with_lm}
# See if we can predict Nathan Creek median flow by neighbour's median flow

# We need to get mean MAD for each neighbour separately in different columns.
# That's so that we can use them in a linear model that looks like this:
# Nathan_Creek_MAD ~ West_MAD + Salmon_Langley_MAD

stats_data = old_ave |> 
  dplyr::select(-mean_percent_mad_neighbours) |> 
  left_join(
    all_dat |> 
      rename(station_numbers = STATION_NUMBER) |> 
      left_join(station_info) |> 
      filter(lubridate::year(Date) <= 1990) |> 
      # Only include West and Salmon Langley stations
      filter(station_numbers %in% c('08MH098','08MH090')) |>
      mutate(Month = lubridate::month(Date, label = T),
             Day = lubridate::day(Date)) |> 
      group_by(Month,Day,station_short_names) |> 
      summarise(mean_percent_MAD = mean(percent_mad)) |> 
      ungroup() |> 
      tidyr::pivot_wider(names_from = station_short_names, values_from = mean_percent_MAD)
  )

data_for_prediction = all_dat |> 
  rename(station_numbers = STATION_NUMBER) |> 
  left_join(station_info) |> 
  filter(lubridate::year(Date) > 1990) |>
  mutate(Month = lubridate::month(Date, label = T),
         Day = lubridate::day(Date)) |> 
  group_by(Month,Day,station_short_names) |> 
  summarise(mean_percent_MAD = mean(percent_mad)) |> 
  ungroup() |> 
  tidyr::pivot_wider(names_from = station_short_names, values_from = mean_percent_MAD)

# lm_results = lm(nathan_flow ~ West + Salmon_Langley + Salmon_Kap + McLennan + Gifford, data = stats_data)

# stats_data_l = stats_data |> 
#   pivot_longer(cols = -c(Month,Day)) |> 
#   mutate(name = replace(name, name == 'nathan_flow', 'Nathan'))

# summary(lm_results)

# # Can run an ANOVA also - I kind of forget the difference, but I think this test groups' relevances?
# aov_results = aov(nathan_flow ~ West + Salmon_Langley + Salmon_Kap + McLennan + Gifford, data = stats_data)
# 
# summary(aov_results)

# Looks like West, Salmon Kap and Gifford are significant.
# BUT, 1990 - 2020 only has Salmon Langley and West. So, looks like 
# we're using West!

lm_selective = lm(mean_percent_mad_nathan ~ West + Salmon_Langley, data = stats_data)

```

## Linear Model

Summary of linear model using West and Salmon_Langley to predict Nathan Creek flow.

```{r}
summary(lm_selective)

# Snap! Only Salmon_Langley is a significant predictor of Nathan Creek mean % MAD... blast. We're down to one station!

# Predict Nathan Creek flow for 1990-2020 using the same linear regression
data_for_prediction$nathan_flow_preds = predict(lm_selective,
        data_for_prediction
        )

data_for_prediction = data_for_prediction |> 
  mutate(my_date = lubridate::ymd(paste0('1990-',Month,'-',Day)))

# Compare the predicted Nathan Creek flows that we predicted with a linear model to those flows predicted by looking at percent change in nearby stations from 1960-1990 to 1990-2020.

```

```{r time_series}
# # Since this is a time series, we probably can't just do a typical linear model... rather ,we can use the fpp3 package to do a time series linear model.
# 
# salmon_langley_dat = all_dat |> 
#   dplyr::filter(STATION_NUMBER == '08MH090') |> 
#   dplyr::select(STATION_NUMBER, Date, Year, percent_mad) #|> 
#   # mutate(Month = lubridate::month(Date)) |> 
#   # mutate(date = make_yearmonth(Year,Month)) |> 
#   # dplyr::select(-c(Date,Year,Month)) |> 
#   # as_tsibble(percent_mad,
#   #            index = Date)
# 
# salmon_langley_dat |> 
#   group_by(Year) |> 
#   summarise(recs_per_year = n()) |> 
#   filter(recs_per_year < 365)
#   
# as.ts(salmon_langley)
# 
# salmon_langley_ts = ts(data = salmon_langley_ts$percent_mad, start=c(1960,1,20), frequency=365)
# # autoplot(salmon_langley_ts, percent_mad)
# 
# stats_data |>
#   mutate(Month = as.numeric(Month),
#          Day = as.numeric(Day)) |>
#   mutate(date = yearmonth(unite(Month,Day))) |>
#   as_tsibble(index = date)
# lin_reg <- model(trends_ts, TSLM(headache ~ ibuprofen))
```

## Comparison of Prediction Methods for Nathan Creek
```{r}
# PLOT
change_in_ave |> 
  mutate(my_date = lubridate::ymd(paste0('1990-',Month,'-',Day))) |> 
  # mutate(change_type = ifelse(percent_change > 0, 'Increase','Decrease')) |>
  ggplot(aes(x = my_date)) + 
  # geom_point(aes(y = percent_change, col = change_type)) +
  geom_line(aes(y = nathan_predicted, col = '% Change Predictions')) +
  geom_line(aes(x = my_date, y = nathan_flow_preds, col = 'Linear Model Predictions'), data = data_for_prediction) + 
    # geom_point(aes(x = lubridate::ymd(paste0('1990-10-03')),
    #              y = oct_3_2022_percent_MAD),
    #          col = 'red') +
  scale_x_date(date_labels = '%b',date_breaks = "1 month") + 
  # scale_y_continuous(limits = c(0,4)) +
  labs(y = 'Predicted % Mean Annual Discharge',
       x = '',
       title = '1990 - 2020 Predicted Median Flow for Nathan Creek',
       subtitle = 'Using two methods: \n1. Percent Change in neighbour streams between 1960-1990\n2. Linear model of Nathan Creek flow explained by neighbour stream flow',
       caption = 'ground-truthed flow on Oct 3 2022',
       fill = 'Method') + 
  theme_minimal() +
  theme(legend.position = 'bottom')

```

## Location of neighbouring stations

```{r}
# Find station coordinates
stat_p = hy_stations(station_numbers) |> 
  st_as_sf(coords = c("LONGITUDE","LATITUDE"),
           crs = 4326)

all_ecos = bcmaps::ecosections() |> 
  sf::st_transform(crs = 4326)

nathan_creek_ecos = all_ecos |> 
  dplyr::filter(sf::st_intersects(geometry, sf::st_union(stat_p), sparse = F))

mypal = leaflet::colorFactor(
  palette = 'RdYlGn',
  domain = c(F,T)
)

leaf_dat = stat_p |> 
  rename(station_numbers = STATION_NUMBER) |> 
  left_join(station_info) |> 
  mutate(usable = ifelse(station_short_names %in% c("Salmon_Langley","West"),T,F))
  
nathan_creek = bcdata::bcdc_query_geodata('freshwater-atlas-stream-network') |> 
  filter(GNIS_NAME == 'Nathan Creek') |> 
  collect() |> 
  sf::st_transform(crs = 4326)

nathan_creek = nathan_creek |> 
  group_by(BLUE_LINE_KEY) |> 
  dplyr::summarise()

library(leaflet)

leaf_dat |> 
  leaflet() %>%
  addTiles() |> 
  addPolygons(
    data = nathan_creek_ecos,
    color = 'purple',
    fillColor = 'purple',
    fillOpacity = 0.1
  ) |> 
  addPolylines(
    data = nathan_creek[1,],
    label = 'Nathan Creek'
  ) |>
  addCircleMarkers(
    color = ~mypal(usable),
    opacity = 0.95,
    fillOpacity = 0.95,
    label = ~station_short_names
  ) |> 
  addLegend(
    pal = mypal,
    values = leaf_dat$usable,
    title = 'Data in both time periods'
  )
```

```{r}
## Spatial Analyses {.tabset}

### Station Locations
# nathan_station = tidyhydat::hy_stations(station_number = station_numbers[1]) |> st_as_sf(coords = c("LONGITUDE","LATITUDE"), crs = 4326)
# 
# # merritt = tibble(
# #   lat = 50.11036330530752, 
# #   lon = -120.78570288394391
# # ) |> 
# #   st_as_sf(coords = c('lon','lat'), crs = 4326)
# # 
# # nicola_stations = hy_stations() |> 
# #   filter(str_detect(STATION_NAME, 'NICOLA')) |> 
# #   st_as_sf(coords = c("LONGITUDE","LATITUDE"), crs = 4326)
# # 
# # nicola_stations$dist_to_merritt = as.numeric(st_distance(nicola_stations, merritt))
# # 
# # nicola_stations |> 
# #   arrange(dist_to_merritt) |> View()
# 
# merritt_station = hy_stations('08LG007') |> 
#   st_as_sf(coords = c("LONGITUDE","LATITUDE"), crs = 4326)
# 
# all_ecoregions = bcmaps::ecoregions()
# 
# all_ecoregions = all_ecoregions |> 
#   st_transform(crs = 4326) |> 
#   st_join(nathan_station |> 
#             dplyr::select(STATION_NAME), st_intersects)
# 
# nathan_ecoregion = all_ecoregions |> 
#   filter(!is.na(STATION_NAME))
# 
# merritt_ecoregion =  all_ecoregions |> 
#   dplyr::select(-STATION_NAME) |> 
#   st_join(merritt_station |> 
#             dplyr::select(STATION_NAME), st_intersects) |> 
#   filter(!is.na(STATION_NAME))
# 
# ecoregions = nathan_ecoregion |> 
#   bind_rows(merritt_ecoregion)
# 
# stations = nathan_station |> 
#   bind_rows(merritt_station)
# 
# ggplot() + 
#   geom_sf(data = ecoregions, aes(fill = str_to_title(ECOREGION_NAME))) + 
#   geom_sf(data = stations) + 
#   geom_sf_label_repel(data = stations, aes(label = str_to_title(STATION_NAME))) +
#   # ggthemes::theme_map() + 
#   labs(fill = 'Ecoregion Name')
```

```{r}
### 1960 - 1990 Flow Comparison

# merritt_dat = tidyhydat::hy_daily_flows(station_number = '08LG007') |> 
#   filter(lubridate::year(Date) <= 1990, lubridate::year(Date) >= 1960) |> 
#   mutate(Month = lubridate::month(Date, label = T),
#          Day = lubridate::day(Date)) |> 
#   group_by(Month,Day) |> 
#   summarise(merritt_flow = median(Value)) |> 
#   ungroup()
# 
# ecoreg_comp_dat = merritt_dat |> 
#   left_join(nathan_data) |> 
#   mutate(my_date = lubridate::ymd(paste0('1990-',Month,'-',Day)))
# 
# ggplot() + 
#   geom_line(aes(y = merritt_flow, x = my_date, col = 'Merritt median flow'),
#             data = ecoreg_comp_dat) +
#   geom_line(aes(y = nathan_flow, x = my_date, col = 'Nathan median flow'),
#             data = ecoreg_comp_dat)  +
#   scale_x_date(date_labels = '%b',date_breaks = "1 month") + 
#   labs(y = 'Median Flow (m^3/s)',
#        x = '') + 
#   labs(col = 'Stream Group') + 
#   theme_minimal() +
#   theme(legend.position = 'bottom')
```


